Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-05-27 talk/dls2014/paper/paper.tex
add plot to paper
add test

@@

>>>>

There are several sources of extra memory requirements in our
STM system. First, we need to keep track of the state an object
is in. We do this using flags and an overflow number. Both currently
fit in an additional header of 4~bytes per object.

Second, there are areas in memory private to each segment (see
section \ref{sub:Setup}). The Nursery for example is 4~MiB in
size. Additionally, the area used for the read markers is lazily
mapped by the kernel and only needed for objects in the old object
space. Thus, it can be at most the total size of memory used by
old objects divided by 16.

Third, since we do copy on write, if all objects were to be
written to at the same time, all pages would need to be privatised
for all objects in the old object space. In that case we would
need the total amount of memory required by old objects multiplied
by $N+1$ (incl. the sharing segment).
\remi{maybe collect some statistics about pages privatised per segment}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1\columnwidth]{plots/richards_mem.pdf}
  \caption{Actual memory managed by the GC and resident set size
    over time in Richards benchmark\label{fig:richards_mem}}
\end{figure}
